---
title: "5. R and Julia Excercise"
author: "m01101000"
output: html_document
---

<body style="background-color:cyan;">

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## ______________________________________________________

```{r}
library(ggplot2)
```

## ______________________________________________________
## a) import the data("iris")

```{r}
data("iris")
```

## ______________________________________________________
## b) make a scatter plot with x-axis: Sepal.Length and y-axis: Sepal.Width, and the species should be shown in different colors

```{r}
ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  labs(x = "Sepal.Length", y = "Sepal.Width") +
  theme_minimal()
```

## ______________________________________________________
## c) add regression line for the previous plot with the whole dataset (regardless of the species)

```{r}
ggplot(data = iris, aes(x = Sepal.Length, y = Sepal.Width, color = Species)) +
  geom_point() +
  geom_smooth(method = "lm", se = FALSE, color = "black") +
  labs(x = "Sepal.Length", y = "Sepal.Width") +
  theme_minimal()
```

## ______________________________________________________
## d) calculate the Pearson correlation for this plot

```{r}
cor(iris$Sepal.Length, iris$Sepal.Width)
```

## ______________________________________________________
## e) make the boxplot for Petal.Width with 3 species separately in the x-axis in different colors

```{r}
ggplot(data = iris, aes(x = Species, y = Petal.Width, fill = Species)) +
  geom_boxplot() +
  labs(x = "Species", y = "Petal.Width") +
  theme_minimal()
```

## ______________________________________________________
## f) make the histogram for Petal.Width with 3 species separately in x-axis in different colors

```{r}
ggplot(data = iris, aes(x = Petal.Width, fill = Species)) +
  geom_histogram(binwidth = 0.2, position = "identity", alpha = 0.7) +
  labs(x = "Petal.Width", y = "Count") +
  theme_minimal()
```

## ______________________________________________________
## g) run the t-test of Petal.Width between setosa and virginica, and give the conclusion if the width is a statistically significant difference between 2 species

```{r}
setosa_width <- iris$Petal.Width[iris$Species == "setosa"]
virginica_width <- iris$Petal.Width[iris$Species == "virginica"]
t_test_result <- t.test(setosa_width, virginica_width)
t_test_result
```